Denoising and decontaminating v2

### 2020-08-03 Scripts/Denoising.all.runs.Rmd
Updated scripts

ASV.nested %>% 
  transmute(Miseq_run,Summary = map(Samples, ~ how.many(ASVtable = .,round = 0)))  -> ASV.summary

@@

```{r summary.file.2}
ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = map(cleaned.tibble, ~ how.many(ASVtable = .,round = "1.Jump"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary 
```

@@

ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = map(Step.1.low.reads, ~ how.many(ASVtable = .,round = "2.Low.nReads"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

@@

ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = map(Step2.tibble, ~ how.many(ASVtable = .,round = "3.Positives"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

@@

occ.results %>% 
  left_join(ASV.nested %>% 
              select(Step2.tibble) %>% 
              unnest(cols = Step2.tibble) %>% 
              group_by(Hash) %>% 
              summarise (tot = sum(nReads))) %>% 
  ggplot(aes(x = cut_interval(real, n = 20))) +
  geom_col(aes(y = tot), fill = "red") +
  labs(x = "",
       y = "Number of Reads")   -> right.plot

@@

ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = map(Step3.tibble, ~ how.many(ASVtable = .,round = "4.Occupancy"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

@@

Let's make the pairwaise distances a long table
```{r}

@@

  ggplot (all.distances.to.plot , aes (fill = Distance.type, x = value)) +
  geom_histogram (position = "dodge", stat = 'density', alpha = 0.9) +
 # facet_wrap( ~ Distance.type) +
  labs (x = "Pairwise dissimilarity", y = "density" ,
        Distance.type = "Distance")

@@

all_distances %>%
  as.tibble() %>% 
  mutate(sample = names(all_distances)) %>% 
  filter(!sample %in% to_write_discarded$sample) %>% 
  separate(sample, into = "event", sep = -3) %>% 
  group_by(event) %>% 
  summarise(cases = n()) %>% 
  separate(event, into = c("Site", "Date"), remove = F) %>% 
  filter(Date != "201703") %>% 
  ggplot()+
  geom_raster(aes(x= Date, y = Site, fill = cases))+
  geom_text(aes(x= Date, y = Site, label = cases))

@@

ASV.nested %>% 
  transmute(Miseq_run, Summary.1 = map(Step4.tibble, ~ how.many(ASVtable = .,round = "5.PCR.dissimilarity"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary 
```

@@

>>>>

ASV.nested %>% 
  transmute(Summary = map(Samples, ~ how.many(ASVtable = .,round = 0)))  -> ASV.summary

@@

```{r summary.file.2}
ASV.nested %>% 
  transmute( Summary.1 = map(cleaned.tibble, ~ how.many(ASVtable = .,round = "1.Jump"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary 
```

@@

ASV.nested %>% 
  transmute( Summary.1 = map(Step.1.low.reads, ~ how.many(ASVtable = .,round = "2.Low.nReads"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

@@

ASV.nested %>% 
  transmute( Summary.1 = map(Step2.tibble, ~ how.many(ASVtable = .,round = "3.Positives"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

@@

occ.results %>% 
  left_join(ASV.nested %>% 
              select(Step2.tibble) %>% 
              unnest(cols = Step2.tibble) %>% 
              group_by(Hash) %>% 
              summarise (tot = sum(nReads))) %>% 
  ggplot(aes(x = cut_interval(real, n = 20))) +
  geom_col(aes(y = tot), fill = "red") +

  labs(x = "",
       y = "Number of Reads")   -> right.plot

@@

ASV.nested %>% 
  transmute(Summary.1 = map(Step3.tibble, ~ how.many(ASVtable = .,round = "4.Occupancy"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary

@@

Let's make the pairwise distances a long table
```{r}

@@

  ggplot (all.distances.to.plot , aes (fill = Distance.type, x = value)) +
  geom_histogram (position = "dodge", stat = 'density', alpha = 0.9) +
  facet_wrap( ~ Distance.type) +
  labs (x = "Pairwise dissimilarity", y = "density" ,
        Distance.type = "Distance")
ggsave("visual.anova.png", dpi = "retina")
```

@@

all_distances %>%
  as.tibble() %>% 
  mutate(sample = names(all_distances)) %>% 
  filter(!sample %in% to_write_discarded$sample) %>% 
  separate(sample, into = "event", sep = -3) %>% 
  group_by(event) %>% 
  summarise(cases = n()) %>% 
  separate(event, into = c("Site", "Date"), remove = F) %>% 
  filter(Date != "201703") %>% 
  mutate(Date = lubridate::ymd(paste0(Date, "01"))) %>% 
  mutate(Area = case_when(Site %in% c("CP", "LK", "FH") ~ "San Juan Island",
                          TRUE                          ~ "Hood Canal"),
         Site = fct_recode(Site, "Cattle Point" = "CP",
                           "Lime Kiln" = "LK",
                           "Friday Harbor" = "FH",
                           "Twanoh" = "TW",
                           "Potlatch"= "PO",
                           "Lilliwaup" = "LL",
                           "Triton Cove"= "TR",
                           "Salsbury Park"= "SA")) -> Coverage.dataset

Coverage.dataset %>% 
  ggplot()+
  geom_raster(aes(x= Date, y = Site, fill = cases))+
  geom_text(aes(x= Date, y = Site, label = cases))

@@

ASV.nested %>% 
  transmute(Summary.1 = map(Step4.tibble, ~ how.many(ASVtable = .,round = "5.PCR.dissimilarity"))) %>% 
  left_join(ASV.summary) %>% 
  mutate(Summary   = map2(Summary, Summary.1, bind_rows)) %>%
  dplyr::select(-Summary.1) -> ASV.summary 
```

@@

# Coverage Table with nReads

```{r}
# Vector with desired order

order.Sites <- c("Salsbury Park", "Triton Cove", "Lilliwaup", "Potlatch", "Twanoh", "Cattle Point", "Lime Kiln", "Friday Harbor")

ASV.nested %>% 
  select(Miseq_run, Step4.tibble) %>% 
  unnest(Step4.tibble) %>% 
  mutate(nReads = as.integer(nReads)) %>% 
  group_by(sample) %>% 
  summarise (nReads = sum(nReads)) %>% 
  separate (sample, into = "event", sep = -3) -> midstep

# As a table
midstep %>% 
  group_by(event) %>% 
  summarise (mean = mean(nReads), max = max(nReads), min = min(nReads), sd = sd(nReads)) %>% 
transmute (event, data = paste0("(", round(mean,0), " +- ", round(sd,0), ")")) %>% 
  right_join(Coverage.dataset) %>% 
  mutate( data = paste0(cases, " ", data)) %>% 
  arrange(Date) %>% 
  mutate (Date = paste(lubridate::month(Date, label = T),
                      lubridate::year(Date),
                      sep= "'")) %>% 
  pivot_wider(names_from = Date, values_from = data, id_cols = c(Area, Site),values_fill = list(data = "") ) %>% 
  slice(match(Site, order.Sites)) %>% 
  kableExtra::kable() %>% 
  kableExtra::kable_styling() %>% 
  kableExtra::collapse_rows(1, valign = "top")

# As a graph
midstep %>% 
  right_join(Coverage.dataset) %>% 
  group_by(event) %>% 
  mutate(mean = mean(nReads),
         sum = sum(nReads)) %>% 
  mutate(Site = factor(Site, levels = order.Sites)) %>% 
  ggplot(aes(x = Date, 
             y = nReads)) +
  geom_boxplot(aes(group=Date),outlier.alpha = 0.5) +
  geom_point(aes(y = sum,
                 size = cases,
                 color = Area)) +
  scale_y_continuous(labels = scales::comma) +
  scale_x_date(labels = function(x){paste(lubridate::month(x, label = T),
                      lubridate::year(x),
                      sep= "'")}) +
  labs(y = "#reads", x = "") +

  facet_wrap(~Site , nrow = 5,dir = "v", drop = T) +
  theme_minimal() +
  theme(axis.title.y = element_text(angle = 0,vjust = 0.5),
        legend.position = c(0.6, 0.2))
